DATA 624 Homework 6

### 2020-03-19 DATA624/HW6.Rmd
Updated HW6.Rmd

**The first lag of the PACF is the only spike which indicates the value of p in the ARIMA model should be 1.  The high first value in the ACF indicates that the p is also one.**

@@

**No.  Because the differencing term (d) is 2.  We should not include it in the model.**

@@

@@

@@

@@

@@

>>>>

**The first lag of the PACF is the only spike which indicates the value of p in the ARIMA model should be 1.  The high first value in the ACF indicates that the d is also one.**

@@

**No.  Based on the [blog post](https://robjhyndman.com/hyndsight/arimaconstants/) by the text book author, since the differencing term (d) is 2 if c = 0 the eventual forecast function (EFF) will follow a straight line with intercept and slope determined by the last few observations.  If c != 0 then the EFF  will follow a quadratic trend.  Opting for the simplier model We should not include it in the model.**

@@

**$(1-\phi_1B) (1-B)^2y_t = c + (1 + \theta_1B)e_t$**

@@

```{r}
fit <- arima(wmurders, order = c(1, 2, 1))
checkresiduals(fit)
```

**The ACF show all autocorrelations are withing acceptable limits, indicating residuals are white noise.  The p-value of the Ljung-Box test also indicate the residuals are white noise.**

@@

```{r}
forecast(fit, h=3) %>%
  kable() %>%
  kable_styling()
```

@@

```{r}
autoplot(forecast(fit, h=3))
```

@@

**Yes auto.arima() gives the same model that I have chosen.**
